Landings by Length for Georges Bank

### 2021-06-18 docs/GBLandingsByLength.Rmd
add html GBLandingsByLength version of rmd for documention

```{r processLandLen, echo=T,eval=F}
process_hydra_GB_comland(channel,comlandData,lengthData)
```

@@

For each species the annual landings (by NEGEAR) which are now apportioned to a population of fish lengths can be aggregated over the size class intervals described in table x (link).

>>>>

```{r processLandLen, echo=T,eval=F}
expanded <- hydra_process_GB_comland(channel,comlandData,lengthData)
```

@@

For each species the annual landings (by NEGEAR) which are now apportioned to fish lengths can be aggregated over the size class intervals described in table x (link) based on the [fleets](https://noaa-edab.github.io/ms-keyrun/GBFleetDecisions.html) the NEGEAR codes are associated with. The Hydra [simulation and estimation](https://github.com/NOAA-EDAB/hydra_sim/wiki) model implements three fleets: demersal, pelagic, and fixed gear. For this model the broader [fleet classification](https://noaa-edab.github.io/ms-keyrun/GBFleetDecisions.html) is aggregated further (Table xxx).

Any NEGEAR gear types that do not neatly fall into any of the three defined fleets (i.e. the `other` category) are assigned to the fleet dominating landings. The proportions of total landings by size class for each fleet can then be calculated.

```{r hydraformat, echo=T, eval= F}
  speciesList <- unique(expanded$species_itis)
  for (itis in speciesList) {
    hydra_format(expanded,mscatch::fleets,itis)
  }
```

```{r hydrafleet, echo=T, eval=T}
mscatch::fleets %>%  kableExtra::kbl() %>%
  kableExtra::kable_styling("hover", full_width = F)
```
